---
title: "project"
author(s): Jezel V., John E., Shelby T.
output: ioslides_presentation
date: "2026-04-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

-   Bullet 1
-   Bullet 2
-   Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## Loading Data 
```{r}
library(jsonlite)

## Character(s) Data 
url1 <- "https://api.api-onepiece.com/v2/characters/en"
characters <- fromJSON(url1)
characters_df <- as.data.frame(characters)
View(characters_df)

## Locations Data
url2 <- "https://api.api-onepiece.com/v2/locates/en"
locations <- fromJSON(url2)
locations_df <- as.data.frame(locations)
View(locations_df)

## Episodes Data 
url3 <- "https://api.api-onepiece.com/v2/episodes/en"
episodes <- fromJSON(url3)
episodes_df <- as.data.frame(episodes)
View(episodes_df)

```

## Data Description 

## Bounty

Which character has the highest bounty in the  series? 

```{r}


```

Which character has the lowest bounty in the series? 
```{r}

```

## Devil Fruits 

## Islands 


How many islands are in East Blue compared to the North Blue?

```{r}
library(dplyr)
library(ggplot2)

blue_counts <- locations_df %>%
  filter(sea_name %in% c("East Blue", "North Blue")) %>%
  count(sea_name)


ggplot(blue_counts, aes(x = sea_name, y = n)) +
  geom_bar(stat = "identity") +
  labs(
    title = "Number of Islands: East Blue vs North Blue",
    x = "Sea",
    y = "Number of Islands"
  )
```

## Characters 
ggplot 

How many memebers are in Strawhats 
``` {r}

```





